---
title: "R Notebook"
output: github_document
author: "Danielle Lawrence"
---

```{r}
library(tidyverse)
```


```{r}
ggplot2::mpg #shows the data in the package ggplot2
```

```{r}
?mpg #gives info of the dataset mpg
```

```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x=displ, y=hwy))
```


3.2.4
1. 
```{r}
ggplot(data=mpg) #it shows a blank map
```

2. There is 234 rows and 11 columns. 

3. The drv variable describes the type engine and trasmission layout: 4WD, rear-wheel, or front-wheel 

4. 
```{r}
ggplot(data=mpg) +
  geom_point(mapping=aes(x=class, y=drv))
```
This is not the right type of plot for this data. Maybe it would be better to have the x and y axis switched. 

3.3.1
1. The "color="blue"" needs to be outside of the aes() but still inside the mapping ().

2. categorical: model, trans, drv, fl, year, cyl, and class
  continuous: displ, cty, and hwy
I can tell by what would be entered as data. 

3. 
```{r}
ggplot(data=mpg) +
  geom_point(mapping=aes(x=displ, y=cty, size= displ), color="blue", shape="diamond")
```

4. It does all of them.

5. 
```{r}
ggplot(data=mpg) +
  geom_point(mapping=aes(x=displ, y=cty), stroke=2)
```
It seems to make the size of the dots bigger. Instead of having them increase as the data increases, it just increases them all the same amount. 


6.
```{r}
ggplot(data=mpg) +
  geom_point(mapping=aes(x=displ, y=cty,colour = displ < 5))
```
It changes the color due to the argument in place. 


3.5.1
1.
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_wrap(~ cty, nrow = 2)
```
It looks like a scatterplot split into parts. 

2.
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = drv, y = cyl))
```
It is discrete values so the blank spot is where there is no data. 

3. 
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(drv ~ .)

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(. ~ cyl)

```
The period decides whether it is columns or rows.

4. 
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_wrap(~ class, nrow = 2)
```
The benefit is to see each type of car on their own graph, without having to type mulitple codes. The disadvantage is not being able to compare them as easily as on one full graph. 


5. 
```{r}
?facet_wrap
?facet_grid
```
nrow and ncol means the number of rows or columns. 
facet_grid is shaped by vars()

6. Because most screens are wider and not taller so it is better to put the most unique as the columns.


3.6.1
1. Line: geom_smooth
  Boxplot: geom_boxplot
  Histogram: geom_histogram
  Area chart: geom_area
  
2.
```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy, color = drv)) + 
  geom_point(show.legend = FALSE) + 
  geom_smooth(se = FALSE) 
```

3. I couldn't get the legend to go away. I tried it in multiple places.

4. Shows the confidence interval or not.

5. They will look the same because the placement of data and mapping don't matter in which plot theyre placed. 
```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_point() + 
  geom_smooth()

ggplot() + 
  geom_point(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_smooth(data = mpg, mapping = aes(x = displ, y = hwy))
```


6. 
```{r}
c <- ggplot(data = mpg, mapping = aes(x = displ, y = hwy, group=drv))

c + geom_point() + geom_smooth(se = FALSE)

c + geom_smooth(se = FALSE) + geom_point()

d <- ggplot(data = mpg, mapping = aes(x = displ, y = hwy))

d + geom_point(aes(colour = drv)) + geom_smooth(aes(colour = drv), se=FALSE)

d + geom_point(aes(colour = drv)) + geom_smooth(se=FALSE)

d + geom_point(aes(colour = drv)) + geom_smooth(aes(linetype=drv), se=FALSE)

d + geom_point(size = 4, colour = "white") + geom_point(aes(colour = drv))
```


3.7.1
1. It is associated with geom_pointrange
For the previous plot you can put 
```{r}
ggplot(diamonds) +
  geom_pointrange(aes(cut, depth, ymin = depth, ymax = depth))
```

2. geom_col allows for any x to be against any y. geom_bar creates two variables. 

3. ?

4. The predicted y for a given x

5. ?


3.8.1
1. Can add jitter to separate points. 

2. It controls the width and heghth of the data

3. geom_count controls the size of the points in relation to frequency. 

4. 
```{r}
ggplot(data = mpg, mapping = aes(x = class, y = displ)) +
  geom_boxplot(aes(color=fl))
```

3.9.1
2. Allows you to control the labels of the plot

3. coord_quickmap shows lines that adjust to a pherical surface, whereas coord_map keeps the straight lines. 

4. There is a positive relationship. The coord_fixed keeps out visual discrepancies. Geom_abline shows the slope of the relationship. 